---
title: "A Data Cleaning Project"
author: "Pranay Aryal"
date: "8/18/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction
This document tries to analyze the data about calls to 911 in Montgomery County, PA. The dataset was downloaded from Kaggle.

Let's load the libraries and read the dataset
```{r echo=TRUE, eval=TRUE, message=FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(DT)
nine <- read_csv('911.csv')
```

Let's see what the column names are and a small chunk of the data
```{r echo=TRUE, eval=TRUE}
names(nine)
```
The columns seem to be latitude, longitude, description, zip code, the title of the 911-emergency, the time of occurrence, the place, address and e

The last column "e" has the same value `r nine$e %>% unique` for all rows, so we will remove it
```{r echo=TRUE, eval=TRUE}
nine$e %>% unique()
nine <- nine %>% select(-e)
```

Let's check if it was removed
```{r echo=TRUE, eval=TRUE}
names(nine)
```

Okay. Let's try to understand the description column. Let's have a look at 3 of them
```{r echo=TRUE, eval=TRUE}
nine$desc %>% head(3)
```
There seems to 

Look for missing or NA values
```{r echo=TRUE, eval=TRUE}
sapply(nine, function(x)is.na(x) %>% table %>% prop.table)
```