---
title: "A Data Cleaning Project"
author: "Pranay Aryal"
date: "8/18/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction
This document tries to analyze the data about calls to 911 in Montgomery County, PA. The dataset was downloaded from Kaggle.

Let's load the libraries and read the dataset
```{r echo=TRUE, eval=TRUE, message=FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(DT)
nine <- read_csv('~/Downloads/911.csv')
```

Let's see what the column names are and a small chunk of the data
```{r echo=TRUE, eval=TRUE}
names(nine)
```
The columns seem to be latitude, longitude, description, zip code, the title of the 911-emergency, the time of occurrence, the place, address and e

The last column "e" has the same value `r nine$e %>% unique` for all rows, so we will remove it
```{r echo=TRUE, eval=TRUE}
nine$e %>% unique()
nine <- nine %>% select(-e)
```

Let's check if it was removed
```{r echo=TRUE, eval=TRUE}
names(nine)
```

Here is some description about the columns

name                | Description
--------------------|--------------------------------
lat                 | Latitude
lng                 | Longitude
desc                | Description of the Emergency Call
zip                 |  Zip code
title               | Title
timeStamp           | YYYY-MM-DD HH:MM:SS
twp                 | Township
addr                | Address
e                   | Dummy variable(always 1)


Okay. Let's try to understand the description column. Let's have a look at 3 of them
```{r echo=TRUE, eval=TRUE}
nine$desc %>% head(3)
```
It is divided into three parts by semicolons. It looks like the first part is a repitition of the address column. Lets make columns out of these. Lets move the station information to another column. Also the time part as well as the township part
```{r echo=T, eval=T} 
nine$station <- unlist(strsplit(nine$desc, ';'))[3]
nine$station <- gsub(' ', '', nine$station)
nine$time_from_desc = unlist(strsplit(nine$desc, ';'))[4]
```
The first part is the street and the second part of the string is township. We can remove both of them from the character vector, Since we have extracted most of the information out of this column, we can discard it fully
```{r echo=T, eval=T}
nine <- nine %>% select(-desc)
```
The columns we are left with now are: `r names(nine)`

##Looking for missing values in the dataset
```{r echo=TRUE, eval=TRUE}
sapply(nine, function(x)is.na(x) %>% table %>% prop.table)
```
